\name{}: machine learning over interaction networks and ontology-based background knowledge predicts drug--target interactions

### 2021-04-18 paper/main.tex
.

\title[\name{}]{\name{}: Combining Bottom-up and top-down approaches
  through graph learning over interaction networks for
  drug-target-interaction prediction} \author[Sample
\textit{et~al}.]{Tilman Hinnerichs\,$^{\text{\sfb 1,}*}$ and Robert
  Hoehndorf\,$^{\text{\sfb 2}}$}
\address{$^{\text{\sf 1}}$Department, Institution, City, Post Code, Country and \\
  $^{\text{\sf 2}}$Computational Bioscience Research Center, Computer,
  Electrical and Mathematical Sciences \& Engineering Division, King
  Abdullah University of Science and Technology, 4700 King Abdullah
  University of Science and Technology, Thuwal 23955, Saudi Arabia.}

@@

\abstract{\textbf{Motivation:} \textit{In silico} drug--target interaction (DTI) prediction is crucial for drug discovery and down-stream tasks, such as drug indication and drug--disease prediction. However, DTI datasets are prone to certain biases, skewing the effective predictive expressiveness over those datasets. Additionally, only few approaches combine phenotypical and molecular features for DTI prediction.\\
\textbf{Results:} We present \name{} to combine molecular features and functional information with protein--protein interaction networks under usage of graph convolutional neural networks, showing that phenotypic information localizes on the interaction network. We hereby focus on protein-centric evaluation, predicting drugs that may target specific targets. We further show that common drug--target interaction datasets contain intrinsic biases, majorly affecting predictive performance of compared models. Additionally, we propose an modified evaluation scheme and metric to circumvent such skews and to better reflect the problem DTI prediction methods aim to solve. \\
\textbf{Availability:} Source code and data used in \name{} are available at \url{https://github.com/THinnerichs/DTI-VOODOO}\\
\textbf{Contact:} \href{tilman.hinnerichs@kaust.edu.sa}{tilman.hinnerichs@kaust.edu.sa}\\
\textbf{Supplementary information:}10264703 Supplementary data are available at \textit{Bioinformatics}
online.}

>>>>

\title[\name{}]{\name{}: machine learning over interaction networks and
  ontology-based background knowledge predicts drug--target
  interactions}
\author[Hinnerichs \& Hoehndorf]{Tilman Hinnerichs\,$^{\text{\sfb 1,}*}$ and Robert
  Hoehndorf\,$^{\text{\sfb 2}}$}
\address{$^{\text{\sf 1}}$Department, Institution, City, Post Code, Country and \\
  $^{\text{\sf 2}}$Computational Bioscience Research Center, Computer,
  Electrical and Mathematical Sciences \& Engineering Division, King
  Abdullah University of Science and Technology, 4700 King Abdullah
  University of Science and Technology, Thuwal 23955, Saudi Arabia.}

@@

\abstract{\textbf{Motivation:} \textit{In silico} drug--target
  interaction (DTI) prediction is crucial for drug discovery and
  down-stream tasks, such as drug indication and drug--disease
  prediction. However, DTI datasets are prone to certain biases,
  skewing the effective predictive expressiveness over those
  datasets. Additionally, only few approaches combine phenotypical and
  molecular features for DTI prediction. \\
  \textbf{Results:} We present \name{} to combine molecular features
  and functional information with protein--protein interaction
  networks under usage of graph convolutional neural networks, showing
  that phenotypic information localizes on the interaction network. We
  hereby focus on protein-centric evaluation, predicting drugs that
  may target specific targets. We further show that common
  drug--target interaction datasets contain intrinsic biases, majorly
  affecting predictive performance of compared models. Additionally,
  we propose an modified evaluation scheme and metric to circumvent
  such skews and to better reflect the problem DTI prediction methods
  aim to solve. \\
  \textbf{Availability:} Source code and data used in \name{} are
  available at \url{https://github.com/THinnerichs/DTI-VOODOO} \\
  \textbf{Contact:}
  \href{tilman.hinnerichs@kaust.edu.sa}{tilman.hinnerichs@kaust.edu.sa}
  \\
  \textbf{Supplementary information:}Supplementary data are
  available at \textit{Bioinformatics} online.}
